\huge \textbf{Parameter Forecasts From CMB Lensing and Galaxy Lensing Power- and Bispectra}

### 2025-04-17 paper/paper_draft.tex
paper changes

\subsection{Parameter Constraints}
For the parameter constraints, even when combining all signals, most of the parameters are poorly constrained (with minimum uncertainties much bigger than their fiducial values). The combination that is well constrained is $H_0$ and $\sigma_8$. Alternatively one can also look at $H_0$ and $S_8$, where $S_8$ is defined as 
\begin{equation*}
    S_8 = \sigma_8 \sqrt{\frac{\Omega_c + \Omega_b}{0.3}}
\end{equation*}
and is commonly found to be a particularly well constrained parameter in weak lensing surveys. The results are essentially the same so we will stick with $\sigma_8$. The constraints and covariances are shown in figures \ref{fig:side_by_side} (a) and (b). In particular, you can see in  the off diagonal plot that combining the CMB and galaxy lensing removes approximate degeneracies in $H_0$, $\sigma_8$ space to create a much smaller $1\sigma$ confidence ellipse. When comparing powerspectra to bispectra constraints in figure \ref{fig:S8const} we see a more mild improvement in constraints when combining the different sources of information.
\begin{figure}[htbp]
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{paramconstraints_sigma8.pdf}
        \caption{Constraints for $H_0$ and $\sigma_8$ for CMB lensing, galaxy lensing, and CMB + galaxy lensing combined. We use the information from both power and bispectra together with $l_{\max}=2000$ in all three cases.
        The confidence ellipses are for $1\sigma$ ($\sim70\%$) certainty.}
        \label{fig:sigma8const}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{paramconstraints_sigma8_diffspectra.pdf}
        \caption{Same as Fig.~\ref{fig:sigma8const}, except comparing constraints from only using power spectra, only bispectra, or both. $S_8$ instead of $\sigma_8$. In all three cases we use CMB $and$ galaxy lensing.}
        \label{fig:S8const}
    \end{subfigure}
    \caption{Side-by-side comparison of parameter constraints.}
    \label{fig:side_by_side}
\end{figure}

>>>>

\subsection{Parameter Constraints}
For the parameter constraints, even when combining all signals, most of the parameters are poorly constrained (with minimum uncertainties much bigger than their fiducial values). The combination that is well constrained is $H_0$ and $\sigma_8$. Alternatively one can also look at $H_0$ and $S_8$, where $S_8$ is defined as 
\begin{equation*}
    S_8 = \sigma_8 \sqrt{\frac{\Omega_c + \Omega_b}{0.3}}
\end{equation*}
and is commonly found to be a particularly well constrained parameter in weak lensing surveys. The results are essentially the same so we will stick with $\sigma_8$. The constraints and covariances are shown in figures \ref{fig:side_by_side} (a) and (b). In particular, you can see in  the off diagonal plot that combining the CMB and galaxy lensing removes approximate degeneracies in $H_0$, $\sigma_8$ space to create a much smaller $1\sigma$ confidence ellipse. When comparing powerspectra to bispectra constraints in figure \ref{fig:S8const} we see a more mild improvement in constraints when combining the different sources of information.
% \begin{figure}[htbp]
%     \centering
%     \begin{subfigure}[t]{0.48\textwidth}
%         \centering
%         \includegraphics[width=\textwidth]{paramconstraints_sigma8.pdf}
%         
%         \label{fig:sigma8const}
%     \end{subfigure}
%     \hfill
%     \begin{subfigure}[t]{0.48\textwidth}
%         \centering
%         \includegraphics[width=\textwidth]{paramconstraints_sigma8_diffspectra.pdf}
%         \caption{Same as Fig.~\ref{fig:sigma8const}, except comparing constraints from only using power spectra, only bispectra, or both. $S_8$ instead of $\sigma_8$. In all three cases we use CMB $and$ galaxy lensing.}
%         \label{fig:S8const}
%     \end{subfigure}
%     \caption{Side-by-side comparison of parameter constraints.}
%     \label{fig:side_by_side}
% \end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/paramconstraints_difftracers.pdf}
    \caption{Constraints for $H_0$ and $\sigma_8$ for CMB lensing, galaxy lensing, and CMB + galaxy lensing combined. We use the information from both power and bispectra together with $l_{\max}=2000$ in all three cases. The confidence ellipses are for $1\sigma$ certainty.}
    \label{fig:difftracer}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/paramconstraints_diffspectra.pdf}
    \caption{Same as Fig. \ref{fig:difftracer}, except comparing constraints from only using power spectra, only bispectra, or both. In all three cases we use CMB $and$ galaxy lensing.}
    \label{fig:diffspectra}
\end{figure}
